Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
Added more to results section

# Preprocessing

@@

```{r filter, include=FALSE}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..), binwidth = .0025) +
  theme_bw() +
  labs(
    title = "Distribution of Power Outputs", subtitle = "Restricted to high irradiance hours of the day",
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

@@

@@

iid_bootstrap_estimates_from_df <- function(df, B = 10000) {
  boot_power <- boot(df$power_out, meanv, B)
  return(boot_power$t)
}

boot_block <- block_bootstrap_estimates_from_df(df_high_irradiance)
boot_block_df <- data.frame(boot = boot_block, type = rep("Block", length(boot_block)))
boot_iid <- iid_bootstrap_estimates_from_df(df_high_irradiance)
boot_iid_df <- data.frame(boot = boot_iid, type = rep("iid", length(boot_iid)))

vis_df <- rbind(boot_block_df, boot_iid_df)

@@

```{r bootstrap-ci, echo=FALSE}
bootstrap_ci_table <- rbind(
c("iid", paste("(", round(iid_ci[1],3),",", round(iid_ci[2],3), ")")),
c("Block", paste("(", round(block_ci[1],3),",", round(block_ci[2], 3), ")"))
)
colnames(bootstrap_ci_table) <- c("Bootstrap Method", "95% CI")
rownames(bootstrap_ci_table) <- c()

bootstrap_ci_table %>% kable(booktabs = TRUE,
caption="95% confidence intervals for the mean simulated power, as generated by each of the two bootstrapping methods.")

@@

HOUR_WINDOW <- 8:19
df_more_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out)) +
  theme_bw()
print(filtered_power_hist)

twelvehr_plot_power <- time_series_irradiance(df_more_irradiance, "power_out", "Power Output", 12)
ggsave("./images/twelvehr_plot_power.png", make_plot_for_pres(twelvehr_plot_power))

day_plot_power <- time_series_irradiance(df, "power_out", "Power Output", 24)
ggsave("./images/day_plot_power.png", make_plot_for_pres(day_plot_power))

# B1 <- df[df$Hour == c(7:10),]$current_output # Hours before peak
# B2 <- df[df$Hour == c(11:14),]$current_output # Peak hours
# B3 <- df[df$Hour == c(15:18),]$current_output # Hours after peak

# nbb(hours, 4) # in order to make b blocks I would need to solve for b = [n/l] (floor) where n is the length of our data and l is 4, so make nbb call l instead of ib

# nbb(hours, 12)

# Could also block instead by hours but by total current output. Peak hours
# would be a frame around the highest output and then hours before and after
# would coincide with that. This would cause the hours to potentially be
# different based on the season/month as months that get dark earlier could see
# peak hours earlier in the day.

# dpeak <- c(B1,B2,B3)
```

>>>>

## Preprocessing

@@

@@

The data is obviously periodic.
Both the GHI values and the simulated output power values
were periodic by day.
Both have a similar shape, 
even with similar random variation,
as is evidenced
by Figure \ref{fig:ghi-ts} and Figure \ref{fig:power-ts}.
This makes sense, as power output is a direct
calculation (on our simulated model)
from the solar radiance values.

@@

It should be noted that the hourly distribution
of values for GHI and simulated power did not have
exactly the same shape,
as evidenced by Figure \ref{fig:ghi-hour-boxplot}
and Figure \ref{power-hour-boxplot}.
Both figures have values that,
on average, move upward throughout the day,
and then down towards zero at night.
Nighttime accounts for the structural zeros seen the figures.
The variation in the values over the day is due to expected
variation in radiation due to the seasons,
and random variation, like cloud cover.
Some of the random variation can be seen in
Figure \ref{fig:ghi-ts} and Figure \ref{fig:power-ts}.
The range of distributions in Figure \ref{power-hour-boxplot}
was used to guide the data filtering described in the next section.

## Data Filtering

```{r filter, include=FALSE}
HOUR_WINDOW_LOW = 8
HOUR_WINDOW_HIGH = 16
HOUR_WINDOW <- HOUR_WINDOW_LOW:HOUR_WINDOW_HIGH

df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
```

Data was filtered to eliminate low- or no-irradiance hours
from the dataset.
The low-irradiance hours can be seen in
Figure \ref{fig:unfiltered-hist}
and Figure \ref{fig:ghi-hour-boxplot}.
Filtering provides a more accurate measure of the power output
during the daytime hours.
The data was filtered to only include hours
between `r HOUR_WINDOW_LOW` and `r HOUR_WINDOW_HIGH`,
on a 24-hour timescale.
The distribution of power output values after filtering
can be seen in Figure \ref{fig:filtered-hist}.

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

iid_bootstrap_estimates_from_df <- function(df, B = 10000) {
  boot_power <- boot(df$power_out, meanv, B)
  return(boot_power$t)
}
```

```{r boot, include=FALSE}
boot_block <- block_bootstrap_estimates_from_df(df_high_irradiance)
boot_block_df <- data.frame(boot = boot_block, type = rep("Block", length(boot_block)))
boot_iid <- iid_bootstrap_estimates_from_df(df_high_irradiance)
boot_iid_df <- data.frame(boot = boot_iid, type = rep("iid", length(boot_iid)))

boot_mean_est <- mean(boot_block)
```

```{r vis, echo=FALSE}
vis_df <- rbind(boot_block_df, boot_iid_df)

@@

```{r bootstrap-ci, echo=FALSE}
bootstrap_ci_table <- rbind(
c("iid", paste("(", round(iid_ci[1],3),",", round(iid_ci[2],3), ")")),
c("Block", paste("(", round(block_ci[1],3),",", round(block_ci[2], 3), ")"))
)
colnames(bootstrap_ci_table) <- c("Bootstrap Method", "95% CI")
rownames(bootstrap_ci_table) <- c()
bootstrap_ci_table %>% kable(booktabs = TRUE,
caption="95% confidence intervals for the mean simulated power, as generated by each of the two bootstrapping methods.")
```

Bootstrapping was carried out with both the
*iid* and block bootstrapping methods.
95\% percentile confidence intervals for the mean power output
based on both methods are shown in Table 1.
It should be noted that the bounds for each method are
similar to one another on an absolute scale,
though on a relative scale of bootstrap estimates,
the *iid* bootstrap produced a smaller interval.
The interval widths for the bootstrap estimates,
along with histograms of the bootstrap estimates,
are shown in Figure \ref{fig:mean-boot-plot}.

The bootstrapped average power value,
based on the block bootstrap,
was `r round(boot_mean_est, 3)` W.
This provides an accurate estimate of the
average power during daylight hours
provided by the physical solar panel model.
In particular, we report the estimated value
from the block bootstrap because
it accounts for time dependence.
In this case the mean value between the two
methods was very similar,
as seen in Figure \ref{fig:mean-boot-plot}.
However, given that we know this boostrapping
method provides a better estimate for the density overall,
it seems more sound to report the block bootstrap estimate.

```{r power-output-est, echo=FALSE}
power_out_est_day = boot_mean_est * length(HOUR_WINDOW)
power_out_est_year = power_out_est_day * 365
```

Based on our block bootstrap estimate,
a solar panel in LA in our configuration
would produce
`r round(power_out_est_day)` Wh
of energy over the course of a day.
The panels would produce
`r round(power_out_est_year)` Wh
or 
`r round(power_out_est_year/1000)` kWh
of energy over the course of one year,
on average.

@@

twelvehr_plot_power <- time_series_irradiance(df_high_irradiance, "power_out", "Power Output", 12)
ggsave("./images/twelvehr_plot_power.png", make_plot_for_pres(twelvehr_plot_power))

day_plot_power <- time_series_irradiance(df, "power_out", "Power Output", 24)
ggsave("./images/day_plot_power.png", make_plot_for_pres(day_plot_power))
```
